%-------------------------
% Author : Ayush Sukhadan Nair
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[colorlinks=true, linkcolor=blue, urlcolor=blue]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ayush Sukhadan Nair} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ (+91) 9321061394 ~ \href{mailto:nairayush45@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  nairayush45@gmail.com} ~ 
    \href{https://www.linkedin.com/in/ayush-nair-b71699284/}{\raisebox{-0.2\height}\faLinkedin\ linkedin.com/in/ayush-nair}  ~
    \href{https://github.com/AyushSNair}{\raisebox{-0.2\height}\faGithub\ github.com/ayushnair}
    \vspace{-8pt}
\end{center}
  
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Fr. C. Rodrigues Institute of Technology}{Vashi, Navi Mumbai}
      {Bachelor of Engineering in Information Technology}{2022 -- 2026}
      \resumeItemListStart
        \resumeItem{CGPA: 9.55/10.0}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {IISER Mohali x TIFR}{Mohali, Punjab}
      {Project Intern}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Currently working on \textbf{development and testing of silicon sensor modules} for \textbf{high-energy physics experiments}.}
        \resumeItem{Involved in \textbf{automating validation of sensor wire bonds} using \textbf{high quality scanner images} and \textbf{ML models}.}
      \resumeItemListEnd

    \resumeSubheading
      {Sports Mentoring Infusion - NGO}{Remote}
      {Backend + Analytics}{June 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Developed and launched \textbf{production-grade Sports Mentoring Infusion (SMI) application} for non-profit organization.}
        \resumeItem{Successfully scaled application to be used by \textbf{admins, students, coaches and volunteers} in the NGO.}
        \resumeItem{Streamlined NGO's \textbf{communication and volunteer management processes} with \textbf{significant real-world impact}.}
      \resumeItemListEnd

    \resumeSubheading
      {IISER Mohali}{Mohali, Punjab}
      {Project Intern}{July 2024 -- June 2025}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Fall Detection system} using \textbf{YOLOv8-OBB + MediaPipe Pose} for real-time human fall detection.}
        \resumeItem{Combined \textbf{YOLOv8 Oriented Bounding Boxes} with \textbf{MediaPipe Pose Estimation} to verify fall predictions.}
        \resumeItem{Created \textbf{healthcare solution} for elderly, disabled individuals, and patients at risk of falling.}
      \resumeItemListEnd

    \resumeSubheading
      {Fr. Conceicao Rodrigues Institute of Technology}{Vashi, Navi Mumbai}
      {Developer Intern}{July 2024 -- June 2025}
      \resumeItemListStart
        \resumeItem{Improved a \textbf{comprehensive college portal} used by entire college community including \textbf{students, faculty, and alumni}.}
        \resumeItem{Implemented \textbf{secure admin registration}, \textbf{event addition functionalities}, and \textbf{event display features}.}
        \resumeItem{Enhanced \textbf{user experience} and \textbf{system reliability} through comprehensive testing and optimization processes.}
      \resumeItemListEnd

    \resumeSubheading
      {RVTechLearn}{Vashi, Navi Mumbai}
      {Developer Intern}{June 2024 -- November 2024}
      \resumeItemListStart
        \resumeItem{Completed \textbf{semantic segmentation models} achieving \textbf{95\% accuracy}.}
        \resumeItem{Trained \textbf{stock prediction model} using \textbf{time series analysis} with \textbf{90\% accuracy}.}
        \resumeItem{Involved in \textbf{data preprocessing}, \textbf{feature engineering}, and \textbf{ML pipeline development}.}
        \resumeItem{Developed \textbf{AI-powered applications} and deployed \textbf{ML models to production}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}


%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{Delta Investments} $|$ \emph{MERN Stack, AI Integration}}{2024}
          \resumeItemListStart
            \resumeItem{Built \textbf{MERN stack-based platform} for smart investment management with comprehensive features.}
            \resumeItem{Integrated \textbf{real-time stock data}, \textbf{learning modules}, and \textbf{Gemini AI} for predictive market analysis.}
            \resumeItem{Features include \textbf{stock \& portfolio tracking}, \textbf{bonds}, \textbf{insurance}, and \textbf{AI-powered auto trading}.}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{VaniConnect: Sign Language to Voice Transcriber} $|$ \emph{Python, Computer Vision, ML}}{2024}
          \resumeItemListStart
            \resumeItem{Developed \textbf{innovative solution} to bridge communication gaps between \textbf{sign language users} and others.}
            \resumeItem{Implemented \textbf{real-time sign language gesture translation} to spoken language using \textbf{computer vision}.}
            \resumeItem{\textbf{Won Summer Project Competition} for this sign language transcription solution.}
          \resumeItemListEnd 
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{Open Source Contribution Tracker \& Analysis} $|$ \emph{React, Node.js, MongoDB}}{2024}
          \resumeItemListStart
            \resumeItem{Built \textbf{full-stack platform} for tracking and analyzing \textbf{open source contributions} with comprehensive analytics.}
            \resumeItem{Implemented \textbf{repository recommendation system} to help users find perfect repos for contribution based on skills and interests.}
            \resumeItem{Developed \textbf{profile creation section} enabling users to showcase their \textbf{open source contributions} on LinkedIn.}
            \resumeItem{Deployed with \textbf{CI/CD pipelines} using \textbf{GitHub Actions} for automated testing and deployment.}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\textbf{Visual-Pulse} $|$ \emph{Python, Business Analytics}}{2024}
          \resumeItemListStart
            \resumeItem{Created \textbf{business graph application} centered around \textbf{business object hierarchy}.}
            \resumeItem{Provided additional \textbf{analytical capabilities} and \textbf{insights for business decision-making}.}
          \resumeItemListEnd 
          \vspace{-13pt}

    \resumeSubHeadingListEnd
  \vspace{8pt}

%-----------LEADERSHIP-----------
\section{Leadership \& Activities}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Computer Society of India - IT Department}{FCRIT Mumbai, India}
      {Treasurer (Core Member)}{2023 -- Present}
      \resumeItemListStart
        \resumeItem{Managing \textbf{financial operations} and \textbf{budgeting} for technical events and workshops.}
        \resumeItem{Coordinating with \textbf{team members} and \textbf{external vendors} for seamless event execution and resource allocation.}
        \resumeItem{Overseeing \textbf{expense tracking} and \textbf{financial reporting} to ensure transparent and efficient fund utilization.}
      \resumeItemListEnd

    \resumeSubheading
      {ETAMAX 2024}{FCRIT}
      {Organizing Committee Member}{2024}
      \resumeItemListStart
        \resumeItem{Enhanced \textbf{creative and management skills} through \textbf{event organization} and \textbf{coordination}.}
        \resumeItem{Collaborated with \textbf{cross-functional teams} to ensure successful execution of technical events and competitions.}
        \resumeItem{Managed \textbf{logistics and participant engagement} contributing to overall event success and positive feedback.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
    \resumeSubHeadingListStart

      \resumeSubheading
        {HackQuinox 2024 - Computer Society of India FCRIT}{Mumbai, India}
        {Top 5 Finalist}{2024}
        \resumeItemListStart
          \resumeItem{Demonstrated advanced \textbf{full-stack development}, \textbf{problem-solving} and \textbf{teamwork skills}.}
        \resumeItemListEnd

      \resumeSubheading
        {Summer Project Competition}{FCRIT}
        {Winner - Sign Language to Voice Transcriber}{2024}
        \resumeItemListStart
          \resumeItem{Recognized for \textbf{innovative communication solution} using \textbf{computer vision} and \textbf{machine learning}.}
        \resumeItemListEnd

      \resumeSubheading
        {Smart India Hackathon}{Government of India}
        {Cleared Internal Round}{2024}
        \resumeItemListStart
          \resumeItem{Selected for \textbf{national-level hackathon} after \textbf{rigorous internal evaluation process}.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, PHP, JavaScript, HTML/CSS, SQL} \\
     \textbf{Frontend}{: React, HTML/CSS, JavaScript} \\
     \textbf{Backend}{: Node.js, Express, MongoDB, PHP} \\
     \textbf{Machine Learning}{: TensorFlow, PyTorch, Scikit-learn, Computer Vision, NLP, Time Series Analysis} \\
     \textbf{Databases}{: MongoDB, MySQL, PostgreSQL} \\
     \textbf{Tools}{: Git, Data Structures, Data Science}
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}
